Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-09-26 paper.tex
fixed big datasets

        \section{Big neuroimaging Datasets}\label{datasets}
            Neuroimaging big data comes in two formats: 1) large images and 2) 
            large datasets. Large images consist of a singular images ranging 
            from 100s of gigabytes to terabytes in size. A well-known example of 
            such an image is the BigBrain \note{cite here}, a histological image 
            of the brain of a healthy 69 year-old man. At its highest resolution
            , it is 1x1x20$\mu$m or 1TB in
            size. Other examples of large images can be found in electron 
            microscopy (EM), polarized light images (PLI) and micro coherence 
            tomography (microCT) \note{need to do more research here.cite}. 
            Images at 
            such high resolution are important to researchers as they provide 
            insights into aspects not otherwise detectible in images at lower 
            resolutions. However, due to their size and lack of resources 
            available to process such images, research on this data remains 
            limited.

            In contrast, large datasets are consists of many images, typically 
            arising from multiple different subjects, that are too big to fit in 
            storage. The images alone being small enough for an average 
            researcher to process. Example of these datasets include the 
            UK Biobank, HCP Project, ADNI dataset,OpenfMRI, amongst many others. 
            These datasets are very large. For instance, the UK Biobank is 
            expected to exceed \note{X} Petabytes in size. As subsets
            of these datasets are manageable for the average researcher to 
            process, much analysis has gone into them. Moreover, unlike for 
            large images, toolkits have been developed for researchers to 
            process this data. However,the toolkits do not enable researchers to 
            process these entire datasets as a whole. Therefore, it is crucial 
            to develop efficient frameworks for the processing of these datasets 
            in order for researchers to harness the data in its entirety.

>>>>

        \section{Big Neuroimaging Datasets}\label{datasets}

            As a result of the rise in datasharing in neuroscience, neuroimaging
            big data has come to fruition. The field of neuroscience has now
            reached a bottleneck where there exists sufficient data to make
            impactful studies, but the software to process these datasets have 
            not evolved with the size of the data.

            Neuroimaging big data comes in two formats: 1) large images and 2) 
            large datasets. Large images consist of a singular images ranging 
            from 100s of gigabytes to terabytes in size. A well-known example of 
            such an image is the BigBrain \note{cite here}, a histological image 
            of the brain of a healthy 69 year-old man. At its highest resolution
            , it is 1x1x20$\mu$m or 1TB in
            size. Other examples of large images can be found in electron 
            microscopy (EM), polarized light images (PLI) and micro coherence 
            tomography (microCT) \note{need to do more research here.cite}. 
            Images at 
            such high resolution are important to researchers as they provide 
            insights into aspects not otherwise detectible in images at lower 
            resolutions. However, due to their size and lack of resources 
            available to process such images, research on this data remains 
            limited.

            In contrast, large datasets are consist of many images acquired from
            multiple subjects, which are too large to be processed in their
            entirety. Notable examples of these datasets include the 
            Alzheimer's Disease Neuroimaging Initiative (ADNI), OpenfMRI, 
            the Autism Brain Imaging Data Exchange (ABIDE), the Consortium for
            Reliability and Reproducibility (CoRR), the Human Connectome Project
            (HCP) and the UK Biobank, with the later
            two being flagship examples of large datasets in neuroimaging.

            The ADNI intiative is a collection of images (structural and 
            functional MRI, PET), urine,
            serum, cerebrospinal fluid biomarkers, as assessments (clinical and
            neuropsychometric) of 800 elderly subjects, which of whom 200 where
            healthy, 400 exhibited mild cognitive impairment and the remaining
            200 showed signs of Alzheimers. Imaging data is available both 
            pre- and post-processed form.

            OpenfMRI is a public repository originally conceived for the sharing
            of task-based fMRI data. Over time, it has grown to include EEG, MEG
            , resting-state fMRI (R-fMRI) and diffusion fMRI. Data made 
            available through
            OpenfMRI are obtained from both healthy and clinical individuals.
            Raw data must be made available for all datasets published to 
            OpenfMRI, however, preprocessed data may also accompany the raw data
            . At present, OpenfMRI houses data of a total 3372 subjects
            originating from 95 studies \note{obtained from website}.

            To promote the advancement of knowledge of Autism Spectrum Disorders
            (ASD), ABIDE was conceived. ABIDE is an open repository of 
            preprocessed data obtained from 1112 R-fMRI datasets.
            In addition to R-fMRI, datasets also contain the corresponding 
            structural MRI and phenotypic data. As data made available in ABIDE
            is preprocessed, standardized pipelines were developed for the 
            preprocessing of the images. Popular neuroimaging processing tools
            such as CIVET, ANTs, and FreeSurfer \note{cite} were used for the 
            preprocessing of structural data, and several other pipelines were
            used for the processing of functional data.

            The CoRR was development as initiative to study and improve the 
            reliability and reproducibility of functional connectomics. The 
            data made available by the Consortium consists of test-retest data 
            obtained from 33 datasets. The repository contains data from 1629 
            subjects, in which anatomical, R-fMRI, dMRI, CBF and ASL scans are 
            available \note{obtained from website}.

            The HCP initiative aimed to characterize the human connectome of 
            1200 healthy adults, ranging from 22 to 35 years of age, by studying
            twins and their non-twin siblings. Data collected for this initiave
            includes structural MRI, R-fMRI, task fMRI and dMRI. MRI data was
            collected using a 3T scanner for all participants, with a 200 
            participants additionally undergoing scans in a higher-resolution 7T
            scanner. MEG and EEG data is available for a subset of the subjects. 
            In addition to imaging data, behavioural and genetic data were also 
            acquired. To faciliate analysis for research groups, HCP made 
            available the raw data, minimally pre-processed data and processed 
            data. Pipelines were developed by the HCP for pre- and post-
            processing. As in ABIDE, these pipelines reused many commonly-used
            neuroimaging tools such as FreeSurfer and FSL for structural data
            and FSL and other tools for functional data. The total amount of
            data made available by the HCP reaches up to nearly 1 Petabyte.

            The UK Biobank is an initiative aimed at the detection of pre-
            symptomatic markers of diseases occuring in middle-aged to elderly 
            populations. The study will gather data from questionnaires, 
            physical and cognative measures and biological samples of 500,000
            individuals. 100,000 of these individuals will additionally be 
            subjected to imaging studies. Imaging modalities used include
            structural MRI, fMRI and dMRI of the brain heart and body; low-dose
            X-ray bone and joint scans; and ultrasound of the carotid arteries.
            As with other initiatives, the UK Biobank makes available both 
            raw and processed data. This data is expected to exceed 0.2 
            Petabytes. Since processed data is provided, the UK Biobank makes 
            available it own pipelines based on tools in FSL, but also plans to
            adapt HCP pipelines from cortical surface extraction in their images
            .

            All these initiave stress the importance of data-sharing and
            large-scale studies for the advancement of science. Many researchers
            are limited to the processing of subsets of the data available as 
            they lack compute and storage resources to process the data in its
            entirety. It is also important to note that many of the pipelines 
            developed by these initiatives made use of popular neuroimaging 
            toolboxes, such as FSL, FreeSurfer, ANTS, CIVET, rather that
            creating their own. Therefore, there is a great need for bigdata
            frameworks that can leverage existing tools for the efficient 
            processing of large-scale datasets. With the availability of such 
            tools, many more research labs will be able to perform
            higher-impact studies \note{reword}.
